---
title: "New Instructions for Mental Imagery - Brain Computer Interfaces"
author: "Daniel Middendorf"
date: "04/06/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
##########################################################
# Import data and libraries
##########################################################

# Downloading required libraries for analysis if they have not been downloaded yet
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(ggplot2)) install.packages("ggplot2", repos = "http://cran.us.r-project.org")
if(!require(cowplot)) install.packages("cowplot", repos = "http://cran.us.r-project.org")
if(!require(knitr)) install.packages("knitr", repos = "http://cran.us.r-project.org")
if(!require(interactions)) install.packages("interactions", repos = "http://cran.us.r-project.org")
if(!require(readxl)) install.packages("readxl", repos = "http://cran.us.r-project.org")
if(!require(rstatix)) install.packages("rstatix", repos = "http://cran.us.r-project.org")
if(!require(psy)) install.packages("psy", repos = "http://cran.us.r-project.org")

# Loading libraries/functions used for the following analyses
library(tidyverse)
library(ggplot2)
library(cowplot)
library(knitr)
library(interactions)
library(readxl)
library(rstatix)
library(readxl)
library(psy)

# Create a function that computes the mode
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

# Loading data 
nimi <- read_excel("C:/Users/Daniel/iCloudDrive/01. College/Honours Bachelor Thesis/Analysis/Analysis Data Daniel.xlsx")

# Make gender/used bci before/ used MI before column numeric (Male,Used MI{BCI before = 1)
nimi$Gender <- ifelse(nimi$Gender == "Male", 1, 0)
nimi$`Used MI before` <- ifelse(nimi$`Used MI before` == "Yes", 1, 0)
nimi$`Used BCI before` <- ifelse(nimi$`Used BCI before` == "Yes", 1, 0)
```

# Descriptive Statistics

## Tables of the Descriptive Statistics

```{r , echo = F}
##########################################################
# Descriptive Sample Data
##########################################################

# Sample Size
samplesize <- data.frame(nrow(nimi))
colnames(samplesize) <- "Sample Size"
kable(samplesize)

# Tables of all the descriptive data regarding the sample
df <- data.frame(Characteristic = c("Gender (Mean)", "Age (Mode)", "Language (Mode)", "Education (Mode)", "Used MI Before (Mean)", "Used BCI Before (Mean)"),
                 Value = c(round(mean(nimi$Gender),2), getmode(nimi$Age), getmode(nimi$Language), getmode(nimi$Education), round(mean(nimi$`Used MI before`),2), round(mean(nimi$`Used BCI before`),2)))

# Table with descriptive variables
descriptives <- kable(df)
descriptives

# Create Table with Age Frequencies
Age <- as.data.frame(table(nimi$Age)) %>% arrange(desc(Freq))
colnames(Age) <- c("Age", "Frequency")
kable(Age)

# Create Table with Language Frequencies
Language <- as.data.frame(table(nimi$Language)) %>% arrange(desc(Freq))
colnames(Language) <- c("Language", "Frequency")
kable(Language)

# Create Table with Language Frequencies
Education <- as.data.frame(table(nimi$Education)) %>% arrange(desc(Freq))
colnames(Education) <- c("Education", "Frequency")
kable(Education)
table(nimi$Age)
table(nimi$Gender)
table(nimi$Education)
```

## Density Diagrams of the Descriptive Variables

```{r Density Diagramms, echo = F, fig.align='center', comment = "", message = F, results='hide',fig.keep='all'}

# Change Lables Education to fit the lables under the plot
nimi$Education[nimi$Education == "Other"] <- "O" # O stands for other school diploma
nimi$Education[nimi$Education == "(Technical) Secondary School Diploma"] <- "TSD" # TSD stands for technical school diploma
nimi$Education[nimi$Education == "University Degree"] <- "UD" # UD stands for University Degree
nimi$Education[nimi$Education == "Doctorate Degree"] <- "DD" # DD stands for Doctorate Degree
nimi$Education[nimi$Education == "Secondary School"] <- "SS" # SS stands for Secondary School Diploma

# Create Density Plot for Gender variable
dGender <- nimi %>% ggplot(aes(Gender)) + geom_bar() + theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # Density Plot for Gender
dAge <- nimi %>% ggplot(aes(Age)) + geom_bar() + theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # Density Plot for Age
dLanguage <- nimi %>% ggplot(aes(Language)) + geom_bar() + theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # Density Plot for Language
dEducation <- nimi %>% ggplot(aes(Education)) + geom_bar() + theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # Density Plot for Education
dMIbefore <- nimi %>% ggplot(aes(`Used MI before`)) + geom_bar() + theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # Density Plot for done Motor Imagery before
dBCIbefore <- nimi %>% ggplot(aes(`Used BCI before`)) + geom_bar() + theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # Density Plot for used a brain-computer interface before

# Merge all Density Plots into one big plot (grid)
density_plots <- plot_grid(dGender, dAge, dLanguage, dEducation, dMIbefore, dBCIbefore)
density_plots
```

# Experiential Realness

```{r Experiential Realness - Creating the Dataframe, echo = F, fig.align='center', comment = "", message = F,fig.keep='all'}
##########################################################
# Experiential Realness - Creating the Dataframe
##########################################################

# Creating the Experiential Realness Dataframe

# Save analysis relevant conditions; Conditions in which the used data is stored
CHI_V <- c(2, 4, 9, 13)
CHI_W <- c(1, 3, 10, 14)
CMC_V <- c(3, 7, 14, 16)
CMC_W <- c(4, 8, 13, 15)
CHI <- c(CHI_V, CHI_W)
CMC <- c(CMC_V, CMC_W)

# All variable are coded positively excelpt the third question of Experiential Realness for Mental Calculation
ER <- data.frame(ER_V_HI = (nimi$ER_V_01[nimi$Condition %in% CHI_V] + nimi$ER_V_02[nimi$Condition %in% CHI_V] + nimi$ER_V_03[nimi$Condition %in% CHI_V])/3,
                 ER_V_MC = (nimi$ER_V_01[nimi$Condition %in% CMC_V] + nimi$ER_V_02[nimi$Condition %in% CMC_V] + -1*nimi$ER_V_03[nimi$Condition %in% CMC_V])/3, 
                 ER_W_HI = (nimi$ER_W_01[nimi$Condition %in% CHI_W] + nimi$ER_W_02[nimi$Condition %in% CHI_W] + nimi$ER_W_03[nimi$Condition %in% CHI_W])/3,
                 ER_W_MC = (nimi$ER_W_01[nimi$Condition %in% CMC_W] + nimi$ER_W_02[nimi$Condition %in% CMC_W] + -1*nimi$ER_W_03[nimi$Condition %in% CMC_W])/3)
ER <- pivot_longer(ER, 'ER_V_HI':'ER_W_MC', names_to = "Condition", values_to = "ER") # Transform data into long format

ER <- data.frame(ER[,2], str_split_fixed(ER$Condition, "_", 3)[,c(2,3)]) # String processing of conditions. Create column with Condition and Type
colnames(ER) <- c("ER", "Condition", "Type") # Create new column names

# Transform conditions into numbers
ER$Condition[ER$Condition == "V"] <- 1 # Video Condition is Coded: Condition 1
ER$Condition[ER$Condition == "W"] <- 0 # Written Condition is Coded: Condition 0

ER$Type[ER$Type == "HI"] <- 1 # Hand Imagery Condition is Coded: Type 1
ER$Type[ER$Type == "MC"] <- 0 # Mental Calculation Condition is Coded: Type 0

ER$Condition <- as.numeric(ER$Condition) # Character number conditions into number number conditions for Condition
ER$Type <- as.numeric(ER$Type) # Character number conditions into number number conditions for Type
```

## Checking Assumptions

Testing the assumptions for experiential realness for motor imagery. 
Checking for normality by plotting  a density plot of the difference between experiential realness for motor imagery scores.
Checking for homogeneity of variances by performing the Levene's test.

```{r Experiential Realness - Testing Assumptions HI, echo = F, fig.align='center', comment = "", message = F,fig.keep='all'}
##########################################################
# Experiential Realness - Testing Assumptions
##########################################################

# Assumptions for t-test Hand Imagery
# Checking for Normality
diff_ER_V_HI <- ER$ER[ER$Condition == 1 & ER$Type == 1] - ER$ER[ER$Condition == 0 & ER$Type == 1]
plot(density(diff_ER_V_HI))

# Checking for Homogeneity t-test Hand Imagery
levene_ER_V_HI <- data.frame(video = ER$ER[ER$Condition == 1 & ER$Type == 1], written = ER$ER[ER$Condition == 0 & ER$Type == 1]) # Creating a Dataframe with only Hand Imagery (Type == 1) with column video and written
levene_ER_V_HI <- gather(levene_ER_V_HI, key = "Condition", value = "ER") # Transforming the dataframe so that it contains a column for condition and corresponding values for experiential realness
# Performing the Levene Test to check for homogeneity
levene_test(levene_ER_V_HI, ER ~ Condition)
```

Testing the assumptions for experiential realness for mental calculation. 
Checking for normality by plotting  a density plot of the difference between experiential realness for motor imagery scores.
Checking for homogeneity of variances by performing the Levene's test.

```{r Experiential Realness - Testing Assumptions MC, echo = F, fig.align='center', comment = "", message = F,fig.keep='all'}

# Assumptions for t-test Mental Calculation
# Checking for Normality
diff_ER_V_MC <- ER$ER[ER$Condition == 1 & ER$Type == 0] - ER$ER[ER$Condition == 0 & ER$Type == 0]
plot(density(diff_ER_V_MC))

# Checking for Homogeneity t-test Mental Calculation
levene_ER_V_MC <- data.frame(video = ER$ER[ER$Condition == 1 & ER$Type == 0], written = ER$ER[ER$Condition == 0 & ER$Type == 0]) # Creating a Dataframe with only Mental Calculation (Type == 0) with column video and written
levene_ER_V_MC <- gather(levene_ER_V_MC, key = "Condition", value = "ER") # Transforming the dataframe so that it contains a column for condition and corresponding values for experiential realness
# Performing the Levene Test to check for homogeneity
levene_test(levene_ER_V_MC, ER ~ Condition)

```

Testing assumptions for the multiple regression model

```{r Experiential Realness - Testing Assumptions Multiple Linear Regression, echo = F, fig.align='center', comment = "", message = F,fig.keep='all'}
# Assumptions for multiple linear regression
modelER <- lm(ER ~ Condition*Type, data = ER) # Regression Model predicting ER by Condition and Type (incl. moderator)
par(mfrow = c(2,2))
plot(modelER) 
```



```{r Experiential Realness - Fitting the Model, echo = F, fig.align='center', comment = "", message = F,fig.keep='all'}
##########################################################
# Experiential Realness - Fitting a Model
##########################################################

# Cronbach's alpha
ER_cronbach <- data.frame(na.omit(c(nimi$ER_V_01, nimi$ER_W_01)), na.omit(c(nimi$ER_V_02,nimi$ER_W_02)),
                 na.omit(c(nimi$ER_V_03[nimi$Condition %in% CHI_V],nimi$ER_W_03[nimi$Condition %in% CHI_W],
                   -1*nimi$ER_V_03[nimi$Condition %in% CMC_V], -1*nimi$ER_W_03[nimi$Condition %in% CMC_W])))
cronbach(ER_cronbach)

# T-Test for Hand Imagery 
t.test(ER$ER[ER$Condition == 1 & ER$Type == 1], ER$ER[ER$Condition == 0 & ER$Type == 1],
       alternative = "greater", paired = T, var.equal = T) # Pooled sample dependent t-test testing a difference in Experiential Realness for Hand Imagery between Written and Video Instruction

# Cohen's D for Hand Imagery
effERHI <- data.frame(video = ER$ER[ER$Condition == 1 & ER$Type == 1], written = ER$ER[ER$Condition == 0 & ER$Type == 1])
effERHI <- gather(effERHI, key = "Condition", value = "ER")
cohens_d(effERHI, ER ~ Condition, paired = T, var.equal = T)

# T-Test for Mental Calculation
t.test(ER$ER[ER$Condition == 1 & ER$Type == 0], ER$ER[ER$Condition == 0 & ER$Type == 0],
       alternative = "greater", paired = T, var.equal = T) # Pooled sample dependent t-test testing a difference in Experiential Realness for Mental Calculation between Written and Video Instruction

# Cohen's D for Hand Imagery
effERMC <- data.frame(video = ER$ER[ER$Condition == 1 & ER$Type == 0], written = ER$ER[ER$Condition == 0 & ER$Type == 0])
effERMC <- gather(effERMC, key = "Condition", value = "ER")
cohens_d(effERMC, ER ~ Condition, paired = T, var.equal = T)

# Creating the Model to test for the interaction effect of task type (MC/HI)
summary(modelER) # More information on the model

probe_interaction(modelER, pred = Condition, modx = Type) # testing the interaction term

# Testing the difference of slopes between video and written for HI
slope_V_ER <- ER %>% filter(Type == 1) %>% lm(ER ~ Condition, data = .) %>% summary()
slope_W_ER <- ER %>% filter(Type == 0) %>% lm(ER ~ Condition, data = .) %>% summary()

slopediff_ER <- (slope_V_ER$coefficients[,1][2] - slope_W_ER$coefficients[,1][2]) / (sqrt(slope_V_ER$coefficients[,2][2]^2 + slope_W_ER$coefficients[,2][2]^2))
pt(slopediff_ER, df = 36, lower.tail = F) # p value for the difference in p values
```


# Subjective Performance

```{r Subjective Performance, echo = F, fig.align='center', comment = "", message = F,fig.keep='all'}

##########################################################
# Subjective Performance - Creating the Dataframe
##########################################################

# Creating the Subjective Performance Dataframe
SP <- data.frame(SP_V_HI = (nimi$SP_V_01[nimi$Condition %in% CHI_V] + nimi$SP_V_02[nimi$Condition %in% CHI_V])/2,
                 SP_V_MC = (nimi$SP_V_01[nimi$Condition %in% CMC_V] + nimi$SP_V_02[nimi$Condition %in% CMC_V])/2, 
                 SP_W_HI = (nimi$SP_W_01[nimi$Condition %in% CHI_W] + nimi$SP_W_02[nimi$Condition %in% CHI_W])/2,
                 SP_W_MC = (nimi$SP_W_01[nimi$Condition %in% CMC_W] + nimi$SP_W_02[nimi$Condition %in% CMC_W])/2)

SP <- pivot_longer(SP, 'SP_V_HI':'SP_W_MC', names_to = "Condition", values_to = "SP") # Transform data into long format

SP <- data.frame(SP[,2], str_split_fixed(SP$Condition, "_", 3)[,c(2,3)]) # String processing of conditions. Create column with Condition and Type

colnames(SP) <- c("SP", "Condition", "Type") # Change new column names

# Transform conditions into numbers
SP$Condition[SP$Condition == "V"] <- 1 # Video Condition is Coded: Condition 1
SP$Condition[SP$Condition == "W"] <- 0 # Written Condition is Coded: Condition 0

SP$Type[SP$Type == "HI"] <- 1 # Hand Imagery Condition is Coded: Type 1
SP$Type[SP$Type == "MC"] <- 0 # Mental Calculation Condition is Coded: Type 0

SP$Condition <- as.numeric(SP$Condition) # Character number conditions into number number conditions for Condition
SP$Type <- as.numeric(SP$Type) # Character number conditions into number number conditions for Type

##########################################################
# Subjective Performance - Testing Assumptions
##########################################################

# Assumptions for t-test Hand Imagery
# Checking for Normality
diff_SP_V_HI <- SP$SP[SP$Condition == 1 & SP$Type == 1] - SP$SP[SP$Condition == 0 & SP$Type == 1]
plot(density(diff_SP_V_HI))

# Checking for Homogeneity t-test Hand Imagery
levene_SP_V_HI <- data.frame(video = SP$SP[SP$Condition == 1 & SP$Type == 1], written = SP$SP[SP$Condition == 0 & SP$Type == 1]) # Creating a Dataframe with only Hand Imagery (Type == 1) with column video and written
levene_SP_V_HI <- gather(levene_SP_V_HI, key = "Condition", value = "SP") # Transforming the dataframe so that it contains a column for condition and corresponding values for subjective performance
# Performing the Levene Test to check for homogeneity
levene_test(levene_SP_V_HI, SP ~ Condition)


# Assumptions for t-test Mental Calculation
# Checking for Normality
diff_SP_V_MC <- SP$SP[ER$Condition == 1 & ER$Type == 0] - SP$SP[SP$Condition == 0 & SP$Type == 0]
plot(density(diff_SP_V_MC))

# Checking for Homogeneity t-test Mental Calculation
levene_SP_V_MC <- data.frame(video = SP$SP[SP$Condition == 1 & SP$Type == 0], written = SP$SP[SP$Condition == 0 & SP$Type == 0]) # Creating a Dataframe with only Mental Calculation (Type == 0) with column video and written
levene_SP_V_MC <- gather(levene_SP_V_MC, key = "Condition", value = "SP") # Transforming the dataframe so that it contains a column for condition and corresponding values for subjective performance
# Performing the Levene Test to check for homogeneity
levene_test(levene_SP_V_MC, SP ~ Condition)

# Assumptions for multiple linear regression
modelSP <- lm(SP ~ Condition*Type, data = SP) # Regression Model predicting ER by Condition and Type (incl. moderator)
plot(modelSP) 

##########################################################
# Subjective Performance - Fitting a Model
##########################################################

# Cronbach's alpha
SP_cronbach <- data.frame(na.omit(c(nimi$SP_V_01, nimi$SP_W_01)),
                          na.omit(c(nimi$SP_V_02,nimi$SP_W_02)),
                          na.omit(c(nimi$SP_V_03, nimi$SP_W_03)))
cronbach(SP_cronbach)

# T-Test for Hand Imagery 
t.test(SP$SP[SP$Condition == 1 & SP$Type == 1], SP$SP[SP$Condition == 0 & SP$Type == 1],
       alternative = "greater", paired = T, var.equal = T) # Pooled sample dependent t-test testing a difference in Subjective Performance for Hand Imagery between Written and Video Instruction

# Cohen's D for Hand Imagery
effSPHI <- data.frame(video = SP$SP[SP$Condition == 1 & SP$Type == 1], written = SP$SP[SP$Condition == 0 & SP$Type == 1])
effSPHI <- gather(effSPHI, key = "Condition", value = "SP")
cohens_d(effSPHI, SP ~ Condition, paired = T, var.equal = T)

# T-Test for Mental Calculation
t.test(SP$SP[SP$Condition == 1 & SP$Type == 0], SP$SP[SP$Condition == 0 & SP$Type == 0],
       alternative = "greater", paired = T, var.equal = T) # Pooled sample dependent t-test testing a difference in Subjective Performance for Mental Calculation between Written and Video Instruction

# Cohen's D for Hand Imagery
effSPMC <- data.frame(video = SP$SP[SP$Condition == 1 & SP$Type == 0], written = SP$SP[SP$Condition == 0 & SP$Type == 0])
effSPMC <- gather(effSPMC, key = "Condition", value = "SP")
cohens_d(effSPMC, SP ~ Condition, paired = T, var.equal = T)

# Creating the Model to test for the interaction effect of task type (MC/HI)
summary(modelSP) # More information on the model
probe_interaction(modelSP, pred = Condition, modx = Type) # testing the interaction term

# Testing the difference of slopes between video and written for HI
slope_V_SP <- SP %>% filter(Type == 1) %>% lm(SP ~ Condition, data = .) %>% summary()
slope_W_SP <- SP %>% filter(Type == 0) %>% lm(SP ~ Condition, data = .) %>% summary()

slopediff_SP <- (slope_V_SP$coefficients[,1][2] - slope_W_SP$coefficients[,1][2]) / (sqrt(slope_V_SP$coefficients[,2][2]^2 + slope_W_SP$coefficients[,2][2]^2))
pt(slopediff_SP, df = 36, lower.tail = F) # p value for the difference in p values

```


# Usability

```{r Usability, echo = F, fig.align='center', comment = "", message = F,fig.keep='all'}

##########################################################
# Usability - Creating the Dataframe
##########################################################

# Creating the Usability Dataframe
U <- data.frame(U_V_HI = (nimi$U_V_01[nimi$Condition %in% CHI_V] +
                  -1 * nimi$U_V_02[nimi$Condition %in% CHI_V] +
                  nimi$U_V_03[nimi$Condition %in% CHI_V] + 
                  nimi$U_V_04[nimi$Condition %in% CHI_V] + 
                  -1 *nimi$U_V_05[nimi$Condition %in% CHI_V]+ 
                  nimi$U_V_06[nimi$Condition %in% CHI_V] +
                  nimi$U_V_07[nimi$Condition %in% CHI_V])/7, 
                U_V_MC = (nimi$U_V_01[nimi$Condition %in% CMC_V] +
                  -1 * nimi$U_V_02[nimi$Condition %in% CMC_V] +
                  nimi$U_V_03[nimi$Condition %in% CMC_V] + 
                  nimi$U_V_04[nimi$Condition %in% CMC_V] + 
                  -1 *nimi$U_V_05[nimi$Condition %in% CMC_V]+ 
                  nimi$U_V_06[nimi$Condition %in% CMC_V] +
                  nimi$U_V_07[nimi$Condition %in% CMC_V])/7,
                U_W_HI = (nimi$U_W_01[nimi$Condition %in% CHI_W] +
                  -1 * nimi$U_W_02[nimi$Condition %in% CHI_W] +
                  nimi$U_W_03[nimi$Condition %in% CHI_W] + 
                  nimi$U_W_04[nimi$Condition %in% CHI_W] + 
                  -1 *nimi$U_W_05[nimi$Condition %in% CHI_W]+ 
                  nimi$U_W_06[nimi$Condition %in% CHI_W] +
                  nimi$U_W_07[nimi$Condition %in% CHI_W])/7,
                U_W_MC = (nimi$U_W_01[nimi$Condition %in% CMC_W] +
                  -1 * nimi$U_W_02[nimi$Condition %in% CMC_W] +
                  nimi$U_W_03[nimi$Condition %in% CMC_W] + 
                  nimi$U_W_04[nimi$Condition %in% CMC_W] + 
                  -1 *nimi$U_W_05[nimi$Condition %in% CMC_W]+ 
                  nimi$U_W_06[nimi$Condition %in% CMC_W] +
                  nimi$U_W_07[nimi$Condition %in% CMC_W])/7)

U <- pivot_longer(U, 'U_V_HI':'U_W_MC', names_to = "Condition", values_to = "U") # Transform data into long format

U <- data.frame(U[,2], str_split_fixed(U$Condition, "_", 3)[,c(2,3)]) # String processing of conditions. Create column with Condition and Type

colnames(U) <- c("U", "Condition", "Type") # Change new column names

# Transform conditions into numbers
U$Condition[U$Condition == "V"] <- 1 # Video Condition is Coded: Condition 1
U$Condition[U$Condition == "W"] <- 0 # Written Condition is Coded: Condition 0

U$Type[U$Type == "HI"] <- 1 # Hand Imagery Condition is Coded: Type 1
U$Type[U$Type == "MC"] <- 0 # Mental Calculation Condition is Coded: Type 0

U$Condition <- as.numeric(U$Condition) # Character number conditions into number number conditions for Condition
U$Type <- as.numeric(U$Type) # Character number conditions into number number conditions for Type

##########################################################
# Usability - Testing Assumptions
##########################################################

# Assumptions for t-test Hand Imagery
# Checking for Normality
diff_U_V <- U$U[U$Condition == 1] - U$U[U$Condition == 0]
plot(density(diff_U_V))

# Checking for Homogeneity t-test Hand Imagery
levene_U_V <- data.frame(video = U$U[U$Condition == 1], written = U$U[U$Condition == 0]) # Creating a Dataframe with only Hand Imagery (Type == 1) with column video and written
levene_U_V <- gather(levene_U_V, key = "Condition", value = "U") # Transforming the dataframe so that it contains a column for condition and corresponding values for Usability
# Performing the Levene Test to check for homogeneity
levene_test(levene_U_V, U ~ Condition)


##########################################################
# Usability - Fitting a Model
##########################################################
# Cronbach's alpha
U_cronbach <- data.frame(na.omit(c(nimi$U_V_01, nimi$U_W_01)),
                         -1*na.omit(c(nimi$U_V_02,nimi$U_W_02)),
                         na.omit(c(nimi$U_V_03, nimi$U_W_03)),
                         na.omit(c(nimi$U_V_04, nimi$U_W_04)),
                         -1*na.omit(c(nimi$U_V_05, nimi$U_W_05)),
                         na.omit(c(nimi$U_V_06, nimi$U_W_06)),
                         na.omit(c(nimi$U_V_07, nimi$U_W_07)))
cronbach(U_cronbach)

# T-Test for Hand Imagery 
t.test(U$U[U$Condition == 1], U$U[U$Condition == 0],
       alternative = "greater", paired = T, var.equal = T) # Pooled sample dependent t-test testing a difference in Usability for Hand Imagery between Written and Video Instruction

# Cohen's D for Hand Imagery
effUHI <- data.frame(video = U$U[U$Condition == 1], written = U$U[U$Condition == 0])
effUHI <- gather(effUHI, key = "Condition", value = "U")
cohens_d(effUHI, U ~ Condition, paired = T, var.equal = T)
```

